\section*{List of Papers}

\subsection*{Notes}
Four papers, two of them published, and two of them in preparation, are central to fundamental investigation of the two water splitting half-reactions essential for the renewable energy revolution - hydrogen evolution and oxygen evolution - using isotope labeling and the chip-based electrochemisry mass spectrometry (EC-MS) system developed at DTU. Paper \ref{Trimarco2018} describes the chip-based EC-MS technique. Paper \ref{Scott2019_HD} will describe the use of this technique to investigate fundamentals of the hydrogen evolution reaction, the simplest reaction in electrocatalysis, which is still not fully understood. Paper \ref{Roy2018} describes the first oxygen evolution isotope-labeling study performed with it, on the industrially used nickel-iron oxy-hydroxide catalyst. Paper \ref{Scott2019_RuO2} will describe a more advanced and fine-tuned set of oxygen labeling experiments on \ch{RuO2} and \ch{IrO2} electrocatalysts, which are relevant for polymer-electrolyte-membrane fuel cell technology. Papers \ref{Trimarco2018} and \ref{Roy2018} are included in published form. A full first draft of Paper \ref{Scott2019_RuO2} is included, whereas only an outline of Paper \ref{Scott2019_HD} is given in the appendix, and the content is best described in Chapter 2 of the thesis.

In addition to the four papers central to this thesis, I have also included the other published papers that I have been involved in during this PhD project. Paper \ref{Nitopi2019} is especially notable among them. It is a review and perspective article for \ch{CO2} reduction on copper. My most important contribution to this work was writing the introduction, which includes an outline of the anthropogenic contribution to the global carbon cycle and strategies to close it. While in the Paper, this outline is used to motivate the direct electrocatalytic reduction of \ch{CO2}, it also motivates more efficient and cost-effective production of hydrogen by water splitting. Because Paper \ref{Nitopi2019} is very long, I have only included the introduction in this thesis.

\subsection*{Papers central to this thesis}
\parindent=0pt

\noindent\textbf{Paper \ref{Trimarco2018}: Enabling Real-Time Detection of Electrochemical Desorption Phenomena with Sub-Monolayer Sensitivity} \hfill page~\pageref{Trimarco2018}

		\underline{Soren B. Scott}*, Daniel B. Trimarco*, Anil H. Thilsted, Jesper Y. Pan, Thomas Pedersen, Ole Hansen, Ib Chorkendorff, and Peter C.K. Vesborg. 
		
		*These authors contributed equally to this work
		
		\textit{Electrochimica Acta}, 2018, 268, 520-530
		
		DOI: 10.1016/j.electacta.2018.02.060

\vspace{5mm}
\noindent\textbf{Paper \ref{Scott2019_HD}: Insights from electrochemical H-D exchange on Pt, Ir, and Cu} \hfill page~\pageref{Scott2019_HD}

		\underline{Soren B. Scott}, Peter C. K. Vesborg, and Ib Chorkendorff

		\textit{In Preparation}


\vspace{5mm}
\noindent\textbf{Paper \ref{Roy2018}: Impact of nanoparticle size and lattice oxygen on water oxidation on \ch{NiFeO$_x$H$_y$}} \hfill page~\pageref{Roy2018}

	\underline{Soren B. Scott}*, Claudie Roy*, Bela Sebok*, Elisabetta M. Fiordaliso, Jakob E. Sørensen, Anders Bodin, Daniel B. Trimarco, Christian D. Damsgaard, Peter C. K. Vesborg, Ole Hansen, Ifan E. L. Stephens, Jakob Kibsgaard and Ib Chorkendorff. 

	*These authors contributed equally to this work
	
	\textit{Nature Catalysis}, 2018, 1(11), 820-829 
	
	DOI: 10.1038/s41929-018-0162-x

\vspace{5mm}
\noindent\textbf{Paper \ref{Scott2019_RuO2}: Mechanistic study of oxygen evolution on \ch{RuO2} down to 60 mV overpotential}\hfill page~\pageref{Scott2019_RuO2}

	\underline{Soren B. Scott}*, Reshma R. Rao*, Choongman M. Moon, Jakob E. S\o rensen, Jakob Kibsgaard, Yang Shao-Horn, and Ib Chorkendorff
	
	*These authors contributed equally to this work
	
	\textit{In Preparation}

\clearpage
\subsection*{Additional papers published during this PhD project}


\noindent\textbf{Paper \ref{Nitopi2019}: Progress and Perspectives of Electrochemical CO2 Reduction on Copper in Aqueous Electrolyte} \hfill page~\pageref{Nitopi2019}

Stephanie A. Nitopi*, Erlend Bertheussen*, \underline{Soren B. Scott}, Xinyan Liu, Albert K. Engstfeld, Sebastian Horch, Brian Seger, Ifan Stephens, Karen Chan, Christopher Hahn, Jens K. Nørskov, Thomas Jaramillo, and Ib Chorkendorff.

*These authors contributed equally to this work

\textit{Chemical Reviews}. XXXX, XXX, XXX-XXX (available as Article ASAP), 2019

DOI: 10.1021/acs.chemrev.8b00705


\vspace{5mm}
\noindent\textbf{Paper \ref{Winiwarter2019}: Towards an Atomistic Understanding of Electrocatalytic Partial Hydrocarbon Oxidation: Propene on Palladium} \hfill page~\pageref{Winiwarter2019}

Anna Winiwarter*, Luca Silva*, \underline{Soren B. Scott}, Kasper Enemark-Rasmussen, Manuel Saric, Daniel B. Trimarco, Peter C. K. Vesborg, Poul G. Moses, Ifan E. L. Stephens, Brian Seger, Jan Rossmeisl, and Ib Chorkendorff.

*These authors contributed equally to this work

\textit{Energy and Environmental Science}, 12, 1055-1067, 2019.

DOI:  10.1039/C8EE03426E


\vspace{5mm}
\noindent\textbf{Paper \ref{Scott2019_GIXRD}: Absence of Oxidized Phases in Cu under CO Reduction Conditions} \hfill page~\pageref{Scott2019_GIXRD}

\underline{Soren B. Scott}, Thomas V. Hogg, Alan T. Landers, Thomas Maagaard, Erlend Bertheussen, John C. Lin, Ryan C. Davis, Jefferey W. Beeman, Drew Higgins, Walter S. Drisdell, Apurva Mehta, Brian J. Seger, Thomas F. Jaramillo, and Ib Chorkendorff.

\textit{ACS Energy Letters}. 4, 803−804, 2019

DOI: 10.1021/acsenergylett.9b00172